---
title: "dataone-repo-maps"
author: "Matt Jones"
date: "10/17/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

# Building a map of DataONE repository locations

We frequently need to update a map of DataONE repositories.  Automate the
process to make it simpler to regenerate and tweak on demand, and as new 
repositories are added.

## Load repository location data

View the first six repository locations (but the rest are in the table).

```{r location-data, echo=FALSE}
repos <- read.csv("dataone-nodes.csv") %>%
    mutate(name=stringi::stri_sub(name,10))
mns <- repos %>% filter(! name == 'UCSB' &! name == 'UNM' &! name == 'ORC')
cns <- repos %>% filter(name == 'UCSB' | name == 'UNM' | name == 'ORC')
head(mns)
```


## DataONE Member Nodes by year of membership

```{r mn-map-by-year, echo=FALSE}
library(leaflet)
mpal <- colorFactor(
  palette = "Blues",
  domain = repos$year
)
leaflet(mns) %>%
  addTiles() %>%
  addProviderTiles("CartoDB.PositronNoLabels") %>%
  addCircleMarkers(~lon, ~lat, stroke=FALSE, fillOpacity = 1, 
                   fillColor = ~colorFactor("Blues", year)(year), popup = ~as.character(description)) %>%
  addLegend("bottomleft", 
            pal = mpal, 
            values = ~year,
            title = "Year",
            opacity = 1)
```

## DataONE Member Nodes
```{r mn-map, echo=FALSE}
leaflet(mns) %>%
  addTiles() %>%
  addProviderTiles("CartoDB.PositronNoLabels") %>%
  addCircleMarkers(~lon, ~lat, stroke=FALSE, fillOpacity = 1, 
                   fillColor = "#882818", popup = ~as.character(description))
```

## DataONE Coordinating Nodes
```{r cn-map, echo=FALSE}
leaflet(cns) %>%
  addTiles() %>%
  addProviderTiles("CartoDB.PositronNoLabels") %>%
  addCircleMarkers(~lon, ~lat, stroke=FALSE, fillOpacity = 1, 
                   fillColor = "#2F536F", popup = ~as.character(description), label = stringi::stri_sub(~name,10), labelOptions = labelOptions(noHide = TRUE, textSize='36pt', textOnly = TRUE, offset = c(20,-12)))
```



