---
title: "dataone-repo-maps"
author: "Matt Jones"
date: "10/17/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

# Building a map of DataONE repository locations

We frequently need to update a map of DataONE repositories.  Automate the
process to make it simpler to regenerate and tweak on demand, and as new 
repositories are added.

## Load repository location data

View the first six repository locations (but the rest are in the table).

```{r location-data, echo=FALSE}
repos <- read.csv("dataone-nodes.csv") %>%
    mutate(name=stringi::stri_sub(name,10))
mns <- repos %>% filter(! name == 'CNUCSB1' &! name == 'CNUNM1' &! name == 'CNORC1')
cns <- repos %>% filter(name == 'CNUCSB1' | name == 'CNUNM1' | name == 'CNORC1')
head(mns)
```


## DataONE Member Nodes by year of membership

```{r mn-map-by-year, echo=FALSE, fig.width=10}
library(leaflet)
color_pal <- c("#8B76A2","#817BA6","#7780AA","#6B84AD","#5E89AE","#518DAD","#4491AC","#3695A9","#2998A5","#1F9BA0","#199E9A","#1CA193","#25A38B","#31A483","#3EA67A","#4BA772","#58A869","#65A960","#72A958")
mpal <- colorFactor(
  palette = color_pal,
  domain = repos$year
)
leaflet(mns) %>%
  addTiles() %>%
  addProviderTiles("CartoDB.PositronNoLabels") %>%
  addCircleMarkers(~lon, ~lat, stroke=FALSE, fillOpacity = 1, radius=7,
                   fillColor = ~colorFactor(color_pal, year)(year), popup = ~as.character(description)) %>%
  addLegend("bottomleft", 
            pal = mpal, 
            values = ~year,
            title = "Year",
            opacity = 1)
```

## DataONE Member Nodes
```{r mn-map, echo=FALSE, fig.width=10in}
leaflet(mns) %>%
  addTiles() %>%
  addProviderTiles("CartoDB.PositronNoLabels") %>%
  addCircleMarkers(~lon, ~lat, stroke=FALSE, fillOpacity = 1,radius=7,
                   fillColor = "#518DAD", popup = ~as.character(description))
```

## Static map

```{r static-map, fig.width=10}
library(sf)
library(ggplot2)
library(rnaturalearth)
library(scales)
mns_4326 <- st_as_sf(mns,
                     coords = c('lon', 'lat'),
                     crs = 4326,
                     remove = F)
mns_robinson <- st_transform(mns_4326, "ESRI:53030")

# Use natural earth for country boundaries
ne_4326 <- ne_countries(returnclass = "sf")
ne_robinson <- st_transform(ne_4326, "ESRI:53030")

ggplot() +
    geom_sf(data = ne_robinson, aes(fill = pop_est)) +
    geom_sf(data = mns_robinson, aes(color = year)) +
    scale_fill_continuous(low = "khaki",
                          high =  "firebrick",
                          labels = comma) +
    theme_bw()
 
```

## DataONE Coordinating Nodes
```{r cn-map, echo=FALSE}
leaflet(cns) %>%
  addTiles() %>%
  addProviderTiles("CartoDB.PositronNoLabels") %>%
  addCircleMarkers(~lon, ~lat, stroke=FALSE, fillOpacity = 1, 
                   fillColor = "#2F536F", popup = ~as.character(description), label = stringi::stri_sub(~name,10), labelOptions = labelOptions(noHide = TRUE, textSize='36pt', textOnly = TRUE, offset = c(20,-12)))
```

## Cumulative dataset count

```{r}
library(httr2)
library(jsonlite)
query <- 'https://cn.dataone.org/cn/v2/query/solr/?q=formatType:METADATA+AND+-obsoletedBy:*&fl=identifier,dateUploaded&wt=json&rows=0&start=0&facet=true&facet.range=dateUploaded&facet.range.start=2000-01-01T01:01:01Z&facet.range.end=2023-08-31T24:59:59Z&facet.range.gap=%2B1MONTH'
httr2::request(query) |> 
  httr2::req_perform() |> 
  httr2::resp_body_json()
```


